04_DESeq_sexes

### 2019-09-07 analysis/04_DESeq2_sexes_manipulate.Rmd
set levels for manipuation

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
c.colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
c.countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

# set treatment levels
c.colData$treatment <- factor(c.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))

@@

# ceate new variable for hypothesis testing
c.colData <- c.colData %>%
    mutate(hypothesis = fct_recode(treatment,
                            "anticipation" = "control",
                            "anticipation" = "bldg",
                            "incubation" = "lay",
                            "incubation" = "inc.d3",
                            "incubation" = "inc.d9",
                            "incubation" = "inc.d17",
                            "hatchling.care" = "hatch",
                            "hatchling.care" = "n5",
                            "hatchling.care" = "n9"))

>>>>

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
c.colData <- read.csv("../metadata/00_colData_manipluation.csv", header = T, row.names = 1)
c.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

# set treatment levels

@@

levels(c.colData$treatment)
# "extend"    "m.inc.d17" "m.inc.d3"  "m.inc.d8"  "m.inc.d9"  "m.n2"      "prolong"

# rename some factors
c.colData <- c.colData %>%
    mutate(treatment = fct_recode(treatment,
                            "extend" = "extend",
                            "prolong" = "prolong",
                            "early" = "m.inc.d8",
                            "remove.d03" = "m.inc.d3",
                            "remove.d09" = "m.inc.d9",
                            "remove.d17" = "m.inc.d17",
                            "remove.d20" = "m.n2"))

c.colData$treatment <- factor(c.colData$treatment, levels = maniplevels)
